---
title: "Museums"
output: 
  html_document:
    toc: true
    toc_float: true
   
---


## Hello :) ! 

This report is for checking for free&discounted admission to museums around New York City listd in  [colombia arts initiative](https://artsinitiative.columbia.edu/museums/). The operation hours, contact information and other details in location are from [ google](https://www.google.com/).
*just for practice



```{r setup, include=FALSE}
library(leaflet)
library(tidyverse)
library(rvest)
library(httr)
library(Amelia)
library(reprex)

library(flextable)
library(magrittr)
```

```{r,include=FALSE}
url="https://artsinitiative.columbia.edu/museums/"
museum_name=read_html(url)
```

```{r,include=FALSE}
title_vec=
  museum_name %>% 
  html_nodes(css=".elementor-accordion-title") %>% 
  html_text()
```

```{r,include=FALSE}
location_vec=
  museum_name %>% 
  html_nodes(css="p > strong") %>% 
  html_text()
```


```{r,include=FALSE}
museum_crude = 
  read_csv("./museum_time_4.csv") %>% 
  janitor::clean_names() 

skimr::skim(museum_crude)
missmap(museum_crude, main = "Missing values vs observed")
```

## Map of the Museums
```{r,echo=FALSE}
museum_crude %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~long,~lat,popup= ~as.character(rate),label=~museum)
```
Î
```{r,echo=FALSE}
pal<- colorNumeric("viridis",museum_crude %>% pull(rate))
museum_crude %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron)%>% 
  addCircleMarkers(~long,~lat,radius=1,popup= ~as.character(rate),color=~ pal(rate),label=~museum)

```

## Top 10 rated museums: 

```{r,echo=FALSE,message = FALSE}
top_10=
museum_crude %>%
arrange(desc(rate))%>%
  select(museum,rate,status)%>%
  head(10)
top_10 %>% regulartable() %>% autofit() 

```
## Top 10 most reviewed museums: 

```{r,echo=FALSE,message = FALSE}
top_10=
museum_crude %>%
arrange(desc(comment))%>%
  select(museum,comment,rate,status)%>%
  head(10)
top_10 %>% regulartable() %>% autofit() 

```

## Current opening during the Pandemic

```{r,echo=FALSE, }
open=
  museum_crude %>%
  filter(status=="Open")%>%
  arrange(desc(rate))%>%
  select(museum,status,rate,location,comment)
open %>% regulartable() %>% autofit() 

```


## Operation time and current status for each museum and contact information(ordered by rate):

```{r,echo=FALSE}
contact=
  museum_crude %>%
  arrange(desc(rate))%>%
  select(museum,status,open,closed,phone,web)
knitr::kable(contact)

```


## Link to fast look-ups:

Here is a fast look up link to get options: [Week-Week](week-week.html)

